AIMS Data Platform R Client Notebook Example

### 2019-09-03 docs/detailed-example.Rmd
Tidy up

```{r}
#       ==> paste your key here
MY_API_KEY <- "api-key-for-r-notebook"

@@

```{r}

install.packages("devtools")
devtools::install_git("https://github.com/AIMS/data-platform-r")
library(aimsdataplatform)

@@

```{r}
results <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=64, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
```

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value)
#axis(1, results$dataFrame$time, format(results$dataFrame$time, "%b %d"), las=2)
```

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature")
```

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Davies Reef Platform Air Temperature in 2018", col='green')
```

@@

```{r}
results2 <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
```

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
legend("bottomright", c("Davies Reef", "Bramble Cay"), fill=c("green", "blue"))
```

@@

```{r}
results$citation
results2$citation
```

>>>>

```{r}
# paste your key where it says api-key-for-r-notebook
MY_API_KEY <- "api-key-for-r-notebook"

@@

```{r}
install.packages("devtools")
devtools::install_git("https://github.com/AIMS/data-platform-r")
library(aimsdataplatform)

@@

```{r}
results <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=64, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value)

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature")

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Davies Reef Platform Air Temperature in 2018", col='green')

@@

```{r}
results2 <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
legend("bottomright", c("Davies Reef", "Bramble Cay"), fill=c("green", "blue"))

@@

```{r}
results$citation
results2$citation
